Propositions as Sessions, Mechanically

### 2015-04-12 paper/formalisation.tex
Added the references.

Formalised efforts for proving cut elimination for other logics have adopted a
deep embedding~\cite{??,??,??}, where sequents and derivations are represented
explicitly rather than just the conclusion as in the shallow embedding adopted
here. It is unclear whether the cut elimination theorem can be rescued in the
current setting or not, but previous work suggests it is better to use other
approaches. It is worth noting that \citeauthor{Tews:2013}'s Coq development
significant; about 36,000 lines.

>>>>

Formalised efforts for proving cut elimination for other logics have adopted a
deep embedding~\cite{Tews:2013,Dawson:2010,Dawson:2002}, where sequents and
derivations are represented explicitly rather than just the conclusion as in
the shallow embedding adopted here. It is unclear whether the cut elimination
theorem can be rescued in the current setting or not, but previous work
suggests it is better to use other approaches. It is worth noting that
\citeauthor{Tews:2013}'s Coq development significant; about 36,000 lines.
